Specific leaf mass explains difference in biomass partitioning between woody plant functional types

### 2014-10-22 manuscript/draftpaper.Rnw
Used more data throughout (previously used dataset2, now dataset which also includes woodland, savanna). Bug fixes in manuscript, glitch fixes figures, SI5 better right panel X axis).

\usepackage{amssymb,amsmath}
\usepackage{palatino}
\usepackage{framed}
\usepackage{parskip}
\usepackage{graphicx}
\usepackage[default,osfigures,scale=0.95]{opensans}
\graphicspath{ {./figures/} }
\usepackage{geometry}
\usepackage{authblk}
\usepackage{gensymb}
\geometry{verbose,tmargin=3cm,bmargin=3cm,lmargin=3cm,rmargin=3cm}
\bibliographystyle{plain}

@@

@@

@@

\section{flow}

\begin{itemize}

\item First paragraph
\item Allocation in models, main uncertainties
\item Climate effects on partioning : direct (MAT, MAP), indirect (PFT).
\item Known: gymnosperm vs. angiosperm. Unknown: leaf habit (deciduous vs. evergreen), direct climate, patterns for individual plants
\item BAAD : Largest database, other large datasets are stands or only small plants
\item Root scaling no PFT differences, focus on aboveground
\item LMF, LAR
\item Found very large LMF differences, but convergent LAR
\item decompose into MF/AS, MT/AS, find similar differences in MF/AS but none in MT/AS, suggesting convergent AF/AS between PFTs.
\item No direct climate effects, so shift in PFT captures global patterns in biomass partioning
\item This has implications for allocation in DGVMs, they can be divided into roughly three categories in terms of biomass allocation (allocation fractions, allometric constraints, LAI optimization). Allocation vs. partitioning: the role of leaf and stem turnover.

\end{itemize}

\section{textbits}

@@

We found some evidence for a higher root-shoot ratio ($M_R/M_T$) in deciduous angiosperms (Fig.~\ref{fig:figureSI2}), however differences were small and depended on plant height. We found near-isometric scaling ($M_R \propto H^0.93) (cf. \cite{hui_near_2014, cairns_root_1997}), leading to only small shifts in the root-shoot ratio with increasing height. We did not test for direct climate effects on $M_R/M_T$ due to limited data availability for root biomass.

>>>>

\usepackage{amssymb,amsmath}
\usepackage{palatino}
\usepackage{framed}
\usepackage{parskip}
\usepackage{graphicx}
\usepackage[default,osfigures,scale=0.95]{opensans}
\graphicspath{ {./figures/} }
\usepackage{geometry}
\usepackage{authblk}
\usepackage{gensymb}
%\usepackage{lineno}
\geometry{verbose,tmargin=3cm,bmargin=3cm,lmargin=3cm,rmargin=3cm}
\bibliographystyle{plain}

@@

%\linenumbers

@@

\section*{First paragraph}

@@

% \section{flow}
% 
% \begin{itemize}
% 
% \item First paragraph
% \item Allocation in models, main uncertainties
% \item Climate effects on partioning : direct (MAT, MAP), indirect (PFT).
% \item Known: gymnosperm vs. angiosperm. Unknown: leaf habit (deciduous vs. evergreen), direct climate, patterns for individual plants
% \item BAAD : Largest database, other large datasets are stands or only small plants
% \item Root scaling no PFT differences, focus on aboveground
% \item LMF, LAR
% \item Found very large LMF differences, but convergent LAR
% \item decompose into MF/AS, MT/AS, find similar differences in MF/AS but none in MT/AS, suggesting convergent AF/AS between PFTs.
% \item No direct climate effects, so shift in PFT captures global patterns in biomass partioning
% \item This has implications for allocation in DGVMs, they can be divided into roughly three categories in terms of biomass allocation (allocation fractions, allometric constraints, LAI optimization). Allocation vs. partitioning: the role of leaf and stem turnover.
% 
% \end{itemize}

\section*{Main text}

@@

We found some evidence for a higher root-shoot ratio ($M_R/M_T$) in deciduous angiosperms (Fig.~\ref{fig:figureSI2}), however differences were small and depended on plant height. We found near-isometric scaling ($M_R \propto H^{0.93}$) (cf. \cite{hui_near_2014, cairns_root_1997}), leading to only small shifts in the root-shoot ratio with increasing height. We did not test for direct climate effects on $M_R/M_T$ due to limited data availability for root biomass.
